Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-07 WSSSPE1_report/WSSSPE1_summary_report.tex
small edit

In this section, we discuss some of the software projects as case studies to
better understand the points discussed during the workshop and described in the
previous sections. We dive deeper to find how are they affected by the
sustainability related issues in practice. Additionally, we discuss issues
surrounding people, especially the career paths of original developers and
investigate to answer the question: are the original developers are still
around?

>>>>

In this section, we discuss some of the software projects as case studies to
better understand the points discussed during the workshop and described in the
previous sections. We dive deeper to find how are they affected by the
sustainability related issues in practice. Additionally, we discuss issues
surrounding people, especially the career paths of original developers and
investigate to answer the question: \emph{are the original developers still
around?}
